Invasive lionfish present region-wide variation of allometric growth in the Western Atlantic

### 2018-05-24 docs/Manuscript.Rmd
Close #2 : Added changes to the introduction

Empirical modeling efforts examining the feasibility of establishing fisheries for lionfish involve modeling changes in biomass in response to changes in mortality (*i.e.* culling \citep{cote_2014,barbour_2011,andradibrown_2017}). In this case, biomass represents the sum of all individual fish weights. The individual weight ($W$) of an organism can be estimated from its length using the allometric growth equation, $W = aL^b$, where $L$ is an organism's length and $a$ and $b$ are constants. This length-weight relationship for any given species is an essential component of biomass-based modeling, and can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}. Site-specific parameters are therefore necessary in order to obtain accurate biomass estimates in a given region, especially when research involves identifying the total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016}. Equation parameters for lionfish exist for North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica, but remain unavailable for the central Mexican Caribbean \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.

Here, we review lionfish allometric growth parameters throughout its invasion range and examine spatial differences in the equation constants. We also provide a new pair of parameters specific to the central Meixcan Caribbean. Results suggest there are important regional-scale variations in allometric growth patterns of lionfish, and these differences highlight the importance of using site-specific parameters when developing or informing invasion management strategies.

@@

fit <- ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
  geom_point(size = 3, shape = 21, fill = "steelblue", color = "black") +
  theme_cowplot() +
  labs(x = "Total length (mm)", y = "Total Weight (gr)") +
  theme(text = element_text(family = "Times")) +
  scale_color_brewer(palette = "Set3") +
  theme(text=element_text(family = "Times")) +
  geom_smooth(method = "lm", formula = y ~ I(c*x^b), se = F, color = "black", linetype = "dashed") +
  annotate(geom = "text",
            x = 120, y = 390,
            label = get_eqn(model),
            parse = T,
            size = 4,
            family="Times",
            face="italic") +
  annotate(geom = "text",
            x = 120, y = 350,
            label = get_eqn2(model),
            parse = T,
            size = 4,
            family="Times",
            face="italic") +
  annotate(geom = "text",
            x = 120, y = 310, 
            label = get_rsq(model),
            parse = T,
            size = 4,
            family="Times",
            face="italic")

>>>>

Empirical modeling efforts examining the feasibility of establishing fisheries for lionfish involve modeling changes in biomass in response to changes in mortality (*i.e.* culling). A common way to model this is via age- or length-structured population models \citep{cote_2014,barbour_2011,andradibrown_2017}, which convert fish length or age to weight to then calculate total biomass. Therefore, length-weight relationships are an essential component of biomass-based modeling. However, this relationship can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}. Literature suggests that when length-weight relationships are spatially variable, Site-specific parameters are necessary to obtain accurate biomass estimates. This becomes ingreasingly important when estimating the potential effectiveness (and resources neded) of lionfish culling programs or identifying total biomass available for harvest by fishers \citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}. Genetic analysis of invasive lionfish suggest that two distinct population groups exist \citep{betancurr_2011}, and as such we would expect their biology to differ. Despite the large number of studies reporting site-specific length-weight relationships, no studies have described region-wide differences in these.

The objective of this paper is to describe the spatial pattern of length-weight relationships of lionfish in the Caribbean and Western Atlantic and identify wether these differences are trivial. Length-weight relationships for lionfish exist for North Carolina, Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica, but remain unavailable for the central Mexican Caribbean \citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}. This study also provides the first length-weight relationship for this region.

@@

fit <- ggplot(data = fish, mapping = aes(x = Length, y = Weight)) +
  geom_point(size = 3, shape = 21, fill = "steelblue", color = "black") +
  theme_cowplot() +
  labs(x = "Total length (mm)", y = "Total Weight (gr)") +
  theme(text = element_text(family = "Times")) +
  scale_color_brewer(palette = "Set3") +
  theme(text=element_text(family = "Times")) +
  geom_smooth(method = "lm", formula = y ~ I(c*x^b), se = F, color = "black", linetype = "dashed") +
  annotate(geom = "text",
            x = 125, y = 390,
            label = get_eqn(model),
            parse = T,
            size = 4,
            family="Times",
            face="italic") +
  annotate(geom = "text",
            x = 125, y = 350,
            label = get_eqn2(model),
            parse = T,
            size = 4,
            family="Times",
            face="italic") +
  annotate(geom = "text",
            x = 125, y = 310, 
            label = get_rsq(model),
            parse = T,
            size = 4,
            family="Times",
            face="italic")

### 2018-05-24 docs/Manuscript.tex
Close #2 : Added changes to the introduction

Empirical modeling efforts examining the feasibility of establishing
fisheries for lionfish involve modeling changes in biomass in response
to changes in mortality (\emph{i.e.} culling
\citep{cote_2014,barbour_2011,andradibrown_2017}). In this case, biomass
represents the sum of all individual fish weights. The individual weight
(\(W\)) of an organism can be estimated from its length using the
allometric growth equation, \(W = aL^b\), where \(L\) is an organism's
length and \(a\) and \(b\) are constants. This length-weight
relationship for any given species is an essential component of
biomass-based modeling, and can vary across regions as a response to
biotic (\emph{e.g.} local food availability) and abiotic (\emph{e.g.}
water temperature) conditions \citep{johnson_2016}. Site-specific
parameters are therefore necessary in order to obtain accurate biomass
estimates in a given region, especially when research involves
identifying the total biomass available for harvest by fishers
\citep{barbour_2011,morris_2011,johnston_2015,chin_2016}. Equation
parameters for lionfish exist for North Carolina, Northern and Southern
Gulf of Mexico, the Southern Mexican Caribbean, Bahamas, Little Cayman,
Jamaica, Bonaire, Puerto Rico, and Costa Rica, but remain unavailable
for the central Mexican Caribbean
\citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.

Here, we review lionfish allometric growth parameters throughout its
invasion range and examine spatial differences in the equation
constants. We also provide a new pair of parameters specific to the
central Meixcan Caribbean. Results suggest there are important
regional-scale variations in allometric growth patterns of lionfish, and
these differences highlight the importance of using site-specific
parameters when developing or informing invasion management strategies.

>>>>

Empirical modeling efforts examining the feasibility of establishing
fisheries for lionfish involve modeling changes in biomass in response
to changes in mortality (\emph{i.e.} culling). A common way to model
this is via age- or length-structured population models
\citep{cote_2014,barbour_2011,andradibrown_2017}, which convert fish
length or age to weight to then calculate total biomass. Therefore,
length-weight relationships are an essential component of biomass-based
modeling. However, this relationship can vary across regions as a
response to biotic (\emph{e.g.} local food availability) and abiotic
(\emph{e.g.} water temperature) conditions \citep{johnson_2016}.
Literature suggests that when length-weight relationships are spatially
variable, Site-specific parameters are necessary to obtain accurate
biomass estimates. This becomes ingreasingly important when estimating
the potential effectiveness (and resources neded) of lionfish culling
programs or identifying total biomass available for harvest by fishers
\citep{barbour_2011,morris_2011,johnston_2015,chin_2016,cote_2014}.
Genetic analysis of invasive lionfish suggest that two distinct
population groups exist \citep{betancurr_2011}, and as such we would
expect their biology to differ. Despite the large number of studies
reporting site-specific length-weight relationships, no studies have
described region-wide differences in these.

The objective of this paper is to describe the spatial pattern of
length-weight relationships of lionfish in the Caribbean and Western
Atlantic and identify wether these differences are trivial.
Length-weight relationships for lionfish exist for North Carolina,
Northern and Southern Gulf of Mexico, the Southern Mexican Caribbean,
Bahamas, Little Cayman, Jamaica, Bonaire, Puerto Rico, and Costa Rica,
but remain unavailable for the central Mexican Caribbean
\citep{barbour_2011,fogg_2013,dahl_2014,aguilarperera_2016,sabidoitza_2016,sabidoitz_2016,darling_2011,edwards_2014,chin_2016,deleon_2013,toledohernndez_2014,sandel_2015}.
This study also provides the first length-weight relationship for this
region.
